A Study of Common Bug Fix Patterns in Rust

### 2022-11-28 methodology.tex
capitalizations etc

The second part identifies the context of the modification, that is, the path from the root of the tree to the subtree in which the modification has occured. The third part is the content of the change---terminals and nonterminals. Ruxanne looks for changes within each root-level scope (Rust book\footnote{\url{https://doc.rust-lang.org/reference/items.html}} calls these root-level scopes the \textit{items} of a crate). That is, our assumption is that each change pattern occurs within one root-level scope. In this work, we chose to not handle patterns that involve changes in multiple functions or multiple files. However, our tool detects both continuous and non-continuous line changes within one scope.

>>>>

The second part identifies the context of the modification, that is, the path from the root of the tree to the subtree in which the modification has occured. The third part is the content of the change---terminals and nonterminals. Ruxanne looks for changes within each root-level scope (the Rust book\footnote{\url{https://doc.rust-lang.org/reference/items.html}} calls these root-level scopes the \textit{items} of a crate). That is, our assumption is that each change pattern occurs within one root-level scope. In this work, we chose to not handle patterns that involve changes in multiple functions or multiple files. However, our tool detects both continuous and non-continuous line changes within one scope.
